\documentclass[a4paper, 10pt]{ctexart}
\usepackage{myresume}  % 样式包
\usepackage{hyperref}
\usepackage{gradient-text}

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  % \item {\Calluna (+00) 111-2222-3333}  % 电话号码
  \item {\Calluna luyiren12@gmail.com}  % 电子邮件地址
  \item {\Calluna \url{ https://yiren.lu}}  % 个人主页
\end{flushright}\vspace{-45pt}

\begin{flushleft}  % 在此处替换为您的姓名（如有需要还可包括身份信息）
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{\unskip \gradientRGB{Yiren Lu}{119,66,141}{0,0,0}} } \quad {\Calluna \fontsize{14.5pt}{14.5pt}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
  \section{教育背景}
}{
  
  \eduHeading
  {\unskip Institute of Computing Technology, Chinese Academy of Sciences}{\unskip Beijing, China}
  {\unskip 计算机软件与理论硕士候选人}{ 2022.08 - 至今}
  
  \itemListStart
  
  \myItem{\unskip 导师：孙小明}
  
  \myItem{\unskip 研究领域：量子计算，理论计算机科学}
  
  \itemListEnd
  
  
  \eduHeading
  {\unskip School of Computer Science, Beijing University of Posts and Telecommunications}{\unskip Beijing, China}
  {\unskip 计算机科学与技术工程学士}{ 2018.09 - 2022.07}
  
  \itemListStart
  
  \myItem{\unskip 平均绩点：90.34/100（前5\%）}
  
  \itemListEnd
  
  
  \eduHeading
  {\unskip Rizhao No.1 Middle School}{\unskip Shandong, China}
  {\unskip 高中教育}{ 2015.09 - 2018.06}
  
  
}

% -------------------- PUBLICATIONS --------------------
\sectionBlock{
  \section{发表作品}
}{
  \pubListStart
  \justifying
  \item \textbf{Xiao Yuan}, Hua Li. The Future Urban Transportation Systems: Innovations and Challenges. \textit{Journal of Operations Research and Optimization}, 2024.
  \item Hua Li, \textbf{Xiao Yuan}, John Doe. Optimizing Logistics and Supply Chain Networks Using Machine Learning Techniques. \textit{International Conference on Operations Research and Machine Learning}, 2023.
  \item John Doe, \textbf{Xiao Yuan}, Hua Li. Artificial Intelligence in Healthcare: Transforming Diagnostics and Treatment. \textit{International Conference on HealthTech Innovations}, 2023.
  \pubListEnd
}

% -------------------- PROJECTS --------------------
\sectionBlock{
  \section{项目}
}{
  \projHeading
  {\textbf{Advanced Optimization Techniques for Smart Grid Management}}
  {National Natural Science Foundation of China (NSFC)} {2023.01 - 2024.01}

  \projHeading
  {\textbf{Optimizing Urban Traffic Flow Using AI-Based Predictive Models}}
  {Smart Transportation Innovations Grant} {2021.12 - 2022.12}.
}

% -------------------- AWARDS & HONORS --------------------
\sectionBlock{
  \section{奖项与荣誉}
}{
  \awardListStart
  \justifying
  
  \item \emph{\unskip 中国计算机学会优秀本科生奖}, {中国计算机学会} \hfill 2021.08
  
  \item \emph{\unskip 金牌（排名第6/1000+）}, {中国计算机学会大学生计算机系统与程序设计竞赛（CCSP 2020）} \hfill 2020.10
  
  \item \emph{\unskip 银牌}, {国际大学生程序设计竞赛（ICPC），亚洲东部地区决赛} \hfill 2019.12
  
  \item \emph{\unskip 银牌}, {中国大学生程序设计竞赛（CCPC），桂林现场赛} \hfill 2018.11
  
  \item \emph{\unskip 铜牌}, {全国青少年信息学奥林匹克竞赛（NOI 2017）} \hfill 2017.07
  
  \item \emph{\unskip 银牌}, {全国青少年信息学奥林匹克竞赛冬令营（WC 2017）} \hfill 2017.02
  
  \awardListEnd
}

% -------------------- SKILLS --------------------
\sectionBlock{
\section{技能}
}{
\skillListStart
\justifying
\item \emph{语言}: 中文，英语，法语。
\item \emph{编程}: {\Courier \fontsize{11pt}{11pt}\selectfont Python}, {\Courier \fontsize{11pt}{11pt}\selectfont C++}, {\Courier \fontsize{11pt}{11pt}\selectfont MATLAB}.
\skillListEnd
}

% -------------------- OTHERS --------------------
\sectionBlock{
  \section{学术服务}
}{
  \skillListStart
  \justifying
  \item \emph{评审}: \textit{Quantum Science and Technology}
  \skillListEnd
}

\end{document}
